\documentclass{resume}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Arkapravo Ghosh}
\address{+91 70037 68803 \\ Kolkata, West Bengal, India}
\address{\href{mailto:arkapravoghosh99@gmail.com}{arkapravoghosh99@gmail.com} \\ \href{https://www.linkedin.com/in/arkapravo-ghosh}{www.linkedin.com/in/arkapravo-ghosh} \\ \href{https://github.com/Arkapravo-Ghosh}{github.com/Arkapravo-Ghosh}}

\begin{document}
\vspace{0.8em}

\begin{rSection}{OBJECTIVE}
{Computer Science and Engineering Student seeking an Internship position to continue developing my skills and applying the knowledge I have learnt through my studies.}

\end{rSection}
\vspace{0.8em}
\begin{rSection}{Education}

{\bf Bachelor of Technology in Computer Science and Engineering (IoT, Cybersecurity and Blockchain Technology)}, University of Engineering and Management Kolkata \hfill {Expected 2026}\\
\vspace{0.8em}

{\bf Class 12 CBSE}, Kendriya Vidyalaya No. 1 Saltlake \hfill {2022}\\
\begin{tabular}{>{\bfseries}l l}
Subjects: & Computer Science, Physics, Chemistry, Mathematics, English \\
Marks: & 71.2\%
\end{tabular}

{\bf Class 10 CBSE}, Kendriya Vidyalaya No. 1 Saltlake \hfill {2020}
\begin{tabular}{>{\bfseries}l l}
Subjects: & Science, Mathematics, Social Science, Sanskrit, English \\
Marks: & 83.8\%
\end{tabular}
\end{rSection}
\vspace{0.8em}

\begin{rSection}{EXPERIENCE}
    {\bf DevSecOps Engineer} \hfill {Started on June 2023}\\
    PepHub \hfill {Remote}
    \begin{itemize}
        \item {Worked on Deployment and Configuration of Projects on multiple Cloud Environments.}

        \item {Worked on building Secure CI/CD Pipelines.}

        \item {Built the {\href{https://consultancy.pephub.tech}{PepHub Consultancy Website}}.}
    \end{itemize}
\end{rSection}

\vspace{0.8em}

\begin{rSection}{SKILLS}
\begin{itemize}
    \item \textbf{Platforms:} Linux, Windows \& macOS
    \item \textbf{Frontend \& UI/UX: } HTML, CSS, JS, React, Next \& Figma
    \item \textbf{Backend: } Python, FastAPI, Node \& Express
    \item \textbf{Database: } MySQL/MariaDB \& MongoDB
    \item \textbf{DevOps:} Git \& GitHub, Docker, Docker Compose \& Kubernetes
    \item \textbf{Cloud Computing:} Google Cloud Platform
    \item \textbf{IoT:} Arduino, Raspberry Pi \& Node-RED
\end{itemize}
\end{rSection}
\vspace{0.8em}

\begin{rSection}{PROJECTS}
\begin{itemize}
    \item \textbf{\href{https://github.com/Arkapravo-Ghosh/speech-to-text}{Speech To Text API:}} {Built an Open Source Speech To Text API using Python, FastAPI and OpenAI's Whisper v2 Model from HuggingFace Transformers.}

    \item \textbf{\href{https://github.com/Arkapravo-Ghosh/sample-backend-with-sql}{Sample Backend with SQL:}} {Built a Sample Backend with SQL using Node, Express, MariaDB that can Register, Login and Authenticate Users.}

    \item \textbf{\href{https://github.com/Arkapravo-Ghosh/minecraft-server-resources}{Minecraft Server Resources:}} {Built a repository providing Scripts, Config Files, Tools and other Resources for Easy and Secure Minecraft Server Deployment.}

    \item \textbf{\href{https://raspberry-pi-guide.ark.ark-tech.in}{Raspberry Pi Guide:}} {Built a Raspberry Pi Guide that helps beginners to get started with Raspberry Pi.}

    \item \textbf{\href{https://github.com/Arkapravo-Ghosh/Ark-Linux}{Ark Linux:}} {Built an Open Source Distribution of GNU/Linux based on Arch Linux.}

    \item \textbf{\href{https://github.com/Arkapravo-Ghosh/Smart-Parking-System}{Smart Parking System:}} {Built an Open Source Parking System that updates status of parking slot availability in realtime and displays into a website, made using Raspberry Pi, Node JS, Express JS and React JS.}

    \item \textbf{\href{https://github.com/Arkapravo-Ghosh/attendance-monitoring-system}{Biometric Attendance Management System:}} {Built an Open Source Attendance Management System with an Admin Console that uses Fingerprint Biometrics to collect Attendance.}

    \item \textbf{\href{https://github.com/Arkapravo-Ghosh/asus-fan-mode}{Asus Fan Controller:}} {Built an Open Source Fan Controller for Asus Laptops running Linux.}

    \item \textbf{\href{https://github.com/Arkapravo-Ghosh/asus-micmute-key-led-driver}{Mic Mute Key LED Driver:}} {Built an Open Source Mic Mute Key LED Driver for ASUS Laptops running Linux.}
\end{itemize}
\end{rSection}
\vspace{0.8em}

\begin{rSection}{HOBBIES \& INTERESTS}
\begin{itemize}
    \item Listening to Music
    \item Learning about new Technologies
\end{itemize}
\end{rSection}
\vspace{0.8em}

\begin{rSection}{CERTIFIED COURSES}
\begin{itemize}
    \item \href{https://www.cloudskillsboost.google/public_profiles/dcbf7583-1c68-4d5c-a408-9ad45d93130d}{Google Cloud Study Jams}
\end{itemize}
\begin{itemize}
    \item \href{https://www.cloudskillsboost.google/public_profiles/7594501c-7933-4fba-be9b-2a92ca3ee410}{Google Cloud Platform}
\end{itemize}
\end{rSection}
\end{document}
