\documentclass{resume}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Trisha Mandal}
\address{+91 8670881002 \\ Kolkata, West Bengal, India}
\address{\href{trishamandal0505@gmail.com}{trishamandal462@gmail.com}\\ \href{https://www.linkedin.com/in/trishamandal123/}{www.linkedin.com/in/trishamandal123} \\ \href{https://github.com/trishaamandal}{github.com/trishaamandal}}

\begin{document}
\vspace{-0.4em}

\begin{rSection}{OBJECTIVE}
    {Computer Science and Engineering Student seeking an Internship position to continue developing my skills and applying the knowledge I have learnt through my studies.}

\end{rSection}
\vspace{-0.4em}
\begin{rSection}{Education}

    {\bf Bachelor of Technology in Computer Science and Engineering (IoT, Cybersecurity and Blockchain Technology)}, University of Engineering and Management Kolkata \hfill {Expected 2026}\\
    \vspace{-0.4em}

    {\bf Class 12 WBBSE},Tehatta High School \hfill {2022}\\
    \begin{tabular}{>{\bfseries}l l}
        Subjects: & Biology, Physics, Chemistry, Mathematics, English, Bengali \\
        Marks:    & 84.33\%
    \end{tabular}

    {\bf Class 10 WB WBBSE}, Tehatta Sridam Chandra Balika Vidyalaya \hfill {2020}
    \begin{tabular}{>{\bfseries}l l}
        Subjects: & Science, Mathematics, bengali, Geography, History,English \\
        Marks:    & 84.8\%
    \end{tabular}
\end{rSection}
\vspace{-0.4em}

\begin{rSection}{EXPERIENCE}
    {\bf Wev Developer Engineering Student} \\
    \hfill {Freelancer}
    \begin{itemize}
        \item {Worked on Deployment and Configuration of Projects on multiple  Environments.}
              \vspace{-0.4em}
        \item {Worked on building Secure CI/CD Pipelines.}
              \vspace*{-0.4em}
        \item \href{https://leetcode.com/u/trishumandal/}{Leetcode 200+ Problems solved}

    \end{itemize}
\end{rSection}

\vspace{-0.4em}

\begin{rSection}{SKILLS}
    \begin{itemize}
        \item \textbf{Platforms:} Linux, Windows
              \vspace{-0.4em}
        \item \textbf{Problem-Solving:} Approach data analysis with a problem-solving mindset, identifying patterns and drawing meaningful conclusions.
              \vspace{-0.4em}
        \item \textbf{Frontend \& UI/UX: } HTML, CSS, JS, React,TypeScript
              \vspace{-0.4em}
        \item \textbf{Data Visulization Tools:} Power BI
        \item \textbf{Backend: } Python,Cpp,Node \& Express
              \vspace{-0.4em}
        \item \textbf{Database: } MySQL/MariaDB, MongoDB
              \vspace{-0.4em}
        \item \textbf{DevOps:} Git \& GitHub, Docker, Networking, Cybersecurity
              \vspace{-0.4em}
        \item \textbf{IoT:} Arduino(Basic)
    \end{itemize}
\end{rSection}
\vspace{-0.4em}

\begin{rSection}{PROJECTS}
    \begin{itemize}
        \item \textbf{\href{https://github.com/trishaamandal/Gen-AI}{GEN\_AI:}} {Built an Open Source Speech-to-Text API using Python.}
        \item \textbf{\href{https://github.com/trishaamandal/tracking_number}{Traking Phone Number:}} {Created using Python and FastAPI. The API provides efficient tracking of shipment numbers, integrating with various logistics providers to retrieve real-time status updates and delivery information.}
        \item \textbf{\href{https://github.com/trishaamandal/SoftwareCPE-CVE}{SoftwareCPE CVEMatcher:}} {Built an Open Source Attendance Management System with an Admin Console that uses Fingerprint Biometrics to collect Attendance using Python, MariaDB, Raspberry Pi and Fingerprint Sensor.}
        \item \textbf{\href{https://github.com/trishaamandal/Trafic_Detection}{Trafic Detection:}} {Builtin Python And When the task is to classify a traffic sign, vehicle, or any road-related object from a given image.}
        \item \textbf{\href{https://github.com/trishaamandal/fakenews_detection}{Fake\_News Detection:}} {Built an Open Source Speech-to-Text API using Python.}

    \end{itemize}
\end{rSection}
\vspace{-0.4em}

\begin{rSection}{ FRONTEND PROJECTS}
    \begin{itemize}
        \item \textbf{\href{https://github.com/trishaamandal/CD-studiesPlans}{STUDY WEB:}} {Built with React js}
        \item \textbf{\href{https://github.com/trishaamandal/gameweb}{ONLINE GUN FIGHT GAME:}} { Built with HTML, CSS, JS.}
        \item \textbf{\href{https://github.com/trishaamandal/landingpage_summer}{SUMMER LANDING PAGE:}} {Created with HTML, CSS,JS.}
        \item \textbf{\href{https://github.com/trishaamandal/GYM-group}{GYM WEB:}} {Built with React.}
        \item \textbf{\href{https://github.com/trishaamandal/car_racing}{CAR RACING GAME:}} {Built with javascript.}
        \item \textbf{\href{https://github.com/trishaamandal/Dine_game}{Dine Game:}}{Built with HTML,css,Js}

    \end{itemize}
\end{rSection}
\vspace{-0.4em}

\begin{rSection}{HOBBIES \& INTERESTS}
    \begin{itemize}
        \item Listening to Music \& Singing
              \vspace{-0.4em}
        \item Learning about new Technologies
    \end{itemize}
\end{rSection}
\vspace{-0.4em}

\begin{rSection}{ACTIVITIES}
    \begin{itemize}
        \item \textbf{Web Developer at ChesslaBlab:} Team work and Built Website of {\href{https://github.com/chesslablab}{ChesslaBlab}}  To learn and Play Cless online.
    \end{itemize}
\end{rSection}

\begin{rSection}{CERTIFIED COURSES}
    \begin{itemize}
        \item \href{https://simpli-web.app.link/e/xZ3GpSgkkMb}{SIMPLILEARN CLOUD SECURITY}
        \item \href{https://www.credly.com/badges/6025a592-85b2-4f2b-ae92-93cf83aa0ef6}{badges winner}
        \item \href{https://app.kajabi.com/certificates/1d00b4fe}{Certiprof}
        \item \href{https://www.hackerrank.com/certificates/79c09382a64c}{Hackerrank}
    \end{itemize}
    \vspace{-0.4em}
\end{rSection}
\end{document}
